A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-08-12 paper/elsarticle/elsarticle-template.tex
paper

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp an image to be projected in a manner that it, when projected, appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), a cumbersome manual process called keystone correction---often using software bundled with the projector---can be used to carry out an appropriate corrective image warp. %, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene

@@

@@

A camera can be calibrated by (i) establishing 2D-3D correspondences between pixels in the camera's image plane and the corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output maximum likelihood estimates of the calibration matrix, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D scene points from among the 2D-3D correspondences \cite{Hartley2004,zhang2000flexible}. Calibration images containing a calibration surface such as a chessboard pattern of known dimensions and scale are acquired from varying viewpoints using the camera, to be used to establish the 2D-3D correspondences~$\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is then used to obtain the maximum likelihood estimates~$(\hat{\omega}, \hat{\mathtt{K}}, \{(\hat{\mathtt{R}}_j, \hat{\mathbf{t}}_j)\}), j \in \{ 1, \dots, n_\text{im} \}$ of the lens distortion model coefficients~$\omega$, calibration matrix~$\mathtt{K}$, and rigid body transformations~$(\mathtt{R}_j, \mathbf{t}_j) \in SE(3), j \in \{ 1, \dots, n_\text{im} \}$ that minimize the cumulative reprojection~error
\begin{equation}
\sum_{i=1}^{n_\text{pt}} \sum_{j=1}^{n_\text{im}} d_{\hat{\omega}}(\mathbf{x}_{i,j}, \hat{\mathbf{x}}_{i,j}'),
\label{re}
\end{equation}
where $\hat{\mathtt{R}}_j\mathbf{X}_{i,j} + \hat{\mathbf{t}}_j \in \mathbb{R}^3$ expresses the point~$\mathbf{X}_{i,j}$ in the local coordinate frame of the camera corresponding to the $j^{\text{th}}$~calibration image and $(\hat{\mathbf{x}}_{i,j}'^\top, 1)^\top \sim \hat{\mathtt{K}}(\hat{\mathtt{R}}_j\mathbf{X}_{i,j} + \hat{\mathbf{t}}_j) \in \mathbb{P}^2$ gives the projection~$\hat{\mathbf{x}}_{i,j}' \in \mathbb{R}^2$ in pixels of $\mathbf{X}_{i,j}$ to that image. The function~$d_{\hat{\omega}}$ is a distance function that computes a distance with respect to two pixel positions that it first corrects for lens distortions, in accordance with the lens distortion model coefficients~$\hat{\omega}$ \cite{duane1971close,weng1992camera}. Inverting the rigid body transformation~$(\mathtt{R}_j, \mathbf{t}_j)$ gives the pose~$(\hat{\mathtt{R}}_j^{-1}, -\hat{\mathtt{R}}_j^{-1}\hat{\mathbf{t}}_j^{}) \in SE(3)$ of the $j^{\text{th}}$~camera relative to the 3D scene points of the calibration pattern, with $-\hat{\mathtt{R}}_j^{-1}\hat{\mathbf{t}}_j^{} \in \mathbb{R}^3$ the corresponding center of projection.

@@

The pose of the projector, for each projector calibration image, is provided relative to the 3D points of the pattern---and thus in the coordinate frame of the camera---alongside $\mathtt{K}_\text{proj}$ by the aforementioned optimization procedure. Note that for a fixed projector with steerable mirror, given a projector calibration image, the recovered projector's pose is the pose the projector would have to have had to project to the given target location \textit{in the absence of the mirror}. This is sufficient for our needs in Section~\ref{sec:approach:homography}, and it is in this sense that our system is able to handle a projector equipped with a steerable mirror, without need for modeling the steerable mirror explicitly.

@@

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downwards-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m. At this height, the pixel size (i.e., length or width of a pixel if projected to the scene plane) of the camera was 3.5 mm.

@@

\begin{table}[ht]
\caption{Deviations in measured angles from $90^\circ{}$ across the 15 augmentations produced using our approach.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.25cm}{r p{1.725cm} p{1.725cm}}
\toprule
  & Top Left & Bottom Right \\
\midrule
Mean {\tiny[deg]} & -0.03 & 0.0 \\
Stdev {\tiny[deg]} & 0.4 & 0.34 \\
\bottomrule
\end{tabularx}}
\end{table}

>>>>

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp an image to be projected in a manner that it, when projected, appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), a cumbersome manual process called keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---can be used to carry out an appropriate corrective image warp. %, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene

@@

%Automatic Calibration of a Multiple-Projector Spherical Fish Tank VR Display

@@

A camera can be calibrated by (i) establishing 2D-3D correspondences between pixels in the camera's image plane and the corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output maximum likelihood estimates of the calibration matrix, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D scene points from among the 2D-3D correspondences \cite{Hartley2004,zhang2000flexible}. Calibration images containing a calibration surface such as a chessboard pattern of known dimensions and scale are acquired from varying viewpoints using the camera, to be used to establish the 2D-3D correspondences~$\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is then used to obtain the maximum likelihood estimates~$(\hat{\omega}, \hat{\mathtt{K}}, \{(\hat{\mathtt{R}}_j, \hat{\mathbf{t}}_j)\}), j \in \{ 1, \dots, n_\text{im} \}$ of the lens distortion model coefficients~$\omega$, calibration matrix~$\mathtt{K}$, and rigid body transformations~$(\mathtt{R}_j, \mathbf{t}_j) \in SE(3), j \in \{ 1, \dots, n_\text{im} \}$. These are obtained using bundle adjustment by minimizing the cumulative reprojection error
\begin{equation}
\sum_{i=1}^{n_\text{pt}} \sum_{j=1}^{n_\text{im}} d_{\hat{\omega}}(\mathbf{x}_{i,j}, \hat{\mathbf{x}}_{i,j}'),
\label{re}
\end{equation}
where $\hat{\mathtt{R}}_j\mathbf{X}_{i,j} + \hat{\mathbf{t}}_j \in \mathbb{R}^3$ expresses the point~$\mathbf{X}_{i,j}$ in the local coordinate frame of the camera corresponding to the $j^{\text{th}}$~calibration image and $(\hat{\mathbf{x}}_{i,j}'^\top, 1)^\top \sim \hat{\mathtt{K}}(\hat{\mathtt{R}}_j\mathbf{X}_{i,j} + \hat{\mathbf{t}}_j) \in \mathbb{P}^2$ gives the projection~$\hat{\mathbf{x}}_{i,j}' \in \mathbb{R}^2$ in pixels of $\mathbf{X}_{i,j}$ to that image. The function~$d_{\hat{\omega}}$ is a distance function that computes a distance with respect to two pixel positions that it first corrects for lens distortions, in accordance with the lens distortion model coefficients~$\hat{\omega}$ \cite{duane1971close,weng1992camera}. Inverting the rigid body transformation~$(\mathtt{R}_j, \mathbf{t}_j)$ gives the pose~$(\hat{\mathtt{R}}_j^{-1}, -\hat{\mathtt{R}}_j^{-1}\hat{\mathbf{t}}_j^{}) \in SE(3)$ of the $j^{\text{th}}$~camera relative to the 3D scene points of the calibration pattern, with $-\hat{\mathtt{R}}_j^{-1}\hat{\mathbf{t}}_j^{} \in \mathbb{R}^3$ the corresponding center of projection.

@@

The pose of the projector, for each projector calibration image, is provided relative to the 3D points of the pattern---and thus in the coordinate frame of the camera---alongside $\mathtt{K}_\text{proj}$ by the aforementioned optimization procedure. Note that for a fixed projector with steerable mirror, given a projector calibration image, the recovered projector's pose is the pose the projector would have to have had to project to the given target location \textit{in the absence of the mirror} (i.e., facing directly towards the target location). This is sufficient for our needs in Section~\ref{sec:approach:homography}, and it is in this sense that our system is able to handle a projector equipped with a steerable mirror, without need for modeling the steerable mirror explicitly.

@@

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downwards-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m. At this height, the pixel size (i.e., length or width of a pixel if projected to the scene plane) of the camera was ca.\ 3.5 mm.

@@

\begin{table}[ht]
\caption{Deviations in measured angles from $90^\circ{}$ across the 15 augmentations produced using our approach.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.75cm}{r p{1.95cm} p{1.95cm}}
\toprule
  & Top Left & Bottom Right \\
\midrule
Mean {\tiny[deg]} & -0.03 & 0.0 \\
Stdev {\tiny[deg]} & 0.4 & 0.34 \\
\bottomrule
\end{tabularx}}
\end{table}
